### 2014-02-24 reanalysis/ComBat_original/combat_paper_dataset2_reproduced.rmd
fra iMAc

```{r, results='hide',  message=FALSE}
includelibs = c("pheatmap", "sva", "qvalue", "limma")
lapply(includelibs, require, character.only=T)
```
```{r, cache=TRUE}
datamatrix = as.matrix(read.table("data/dataExample2.txt", sep="\t", header=TRUE))#[1:3000,]# for dev.
sampleannotation = read.table("data/sampleInfoExample2.txt", 
                              sep="\t", header=TRUE, stringsAsFactors=FALSE)
rownames(sampleannotation)=sampleannotation$ArrayName
sampleannotation$Batch=factor(as.character(sampleannotation$Batch)) 
sampleannotation$Cell=factor(as.character(sampleannotation$Cell)) 
# must be discrete for the pheatmap
#table(sampleannotation$ArrayName==dimnames(datamatrix)[[2]]) # ordercheck
datamatrix=datamatrix[,sampleannotation$Type!="WT"]
sampleannotation=sampleannotation[sampleannotation$Type!="WT",]
sampleannotation$Type=factor(sampleannotation$Type)
#dev/debug
useparprior=TRUE
print(dim(datamatrix))

>>>>

```{r, results='hide',  message=FALSE, error=FALSE}
includelibs = c("pheatmap", "sva", "qvalue", "limma")
tmp = lapply(includelibs, require, character.only=T)
print(tmp)
if(any(!unlist(tmp)))
{
  stop( paste("Not able to find all packages. Please install ",
              paste(includelibs[!unlist(tmp)], collapse=", ") )
              )
}
rm(tmp)
```
```{r, cache=TRUE, tidy=FALSE}
datamatrix = as.matrix(read.table("data/dataExample2.txt", sep="\t", header=TRUE))#[1:3000,]#dev.
sampleannotation = read.table("data/sampleInfoExample2.txt", 
                              sep="\t", header=TRUE, stringsAsFactors=FALSE)
rownames(sampleannotation)=sampleannotation$ArrayName
sampleannotation$Batch=factor(as.character(sampleannotation$Batch)) 
sampleannotation$Cell=factor(as.character(sampleannotation$Cell)) 
# must be discrete for the pheatmap
#table(sampleannotation$ArrayName==dimnames(datamatrix)[[2]])#ordercheck
datamatrix=datamatrix[,sampleannotation$Type!="WT"]
sampleannotation=sampleannotation[sampleannotation$Type!="WT",]
sampleannotation$Type=factor(sampleannotation$Type)
#dev/debug
useparprior=TRUE
print(dim(datamatrix))
